Chemical tagging: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-15 papers/clusters.tex
results

Another issue with k-means is that it effectively uses metric
distances in the $D$-space; it presumes Euclidean isotropy.
We choose here to work in the hydrogen-normalized abundance space, the
space of [C/H], [N/H], [O/H], [Na/H], [Mg/H], [Al/H], [Si/H], [S/H],
[K/H], [Ca/H], [Ti/H], [V/H], [Mn/H], [Fe/H], [Ni/H].
But in addition to this, we re-scale these by approximate measurement
precisions obtained by \thecannon\ before running k-means.
This makes the space close to isotropic in measurment uncertainty or
observational precision.

When the k-means results are returned, we construct the $D\times D$ empirical variance tensor for the DWH THIS IS WRONG!

DWH: Citation out to numpy and sklearn.

@@

DWH: Visualize densest clusters.  Some of them are known clusters.
Show examples.

DWH: Do we have streams or other structures?

>>>>

Another issue with k-means is that it effectively uses metric
distances in the $D$-space; it presumes Euclidean isotropy.
We choose here to work in the hydrogen-normalized abundance space, the
space of [C/H], [N/H], [O/H], [Na/H], [Mg/H], [Al/H], [Si/H], [S/H],
[K/H], [Ca/H], [Ti/H], [V/H], [Mn/H], [Fe/H], [Ni/H].
But in addition to this, we re-scale these by approximate measurement
precisions obtained by \thecannon\ before running k-means.
This makes the space close to isotropic in measurement uncertainty or
observational precision.
Importantly we use \emph{only} abundance-space information, and no
positional or velocity information (nor $\teff$ nor $\logg$ nor any
targeting or observational meta-data) as input to the clustering
algorithm.

@@

When the k-means results are returned, the $D\times D$ empirical
variance tensor for the members of each cluster can be constructed,
and an effective density can be computed as the number of points in
the cluster divided by the square-root of the determinant of the
tensor.
This density was used to rank abundance-space overdensities (from highest
to lowest) for visual inspection.
We chose a few interesting cases from many and show them in
\figurename~\ref{fig:M13}, \ref{fig:Pal5}, \ref{fig:Sgr},
\ref{fig:halo}, and \ref{fig:disk}.
The first three of these are known clusters M13, Pal5, and Sagittarius (MKN, ARC, help!).
The fourth is a halo structure with high velocity dispersion and possibly accreted.
The fifth is a thin-disk star-formation feature.
We will discuss these more below.

All of the code for the clustering and visualization is built on numpy
(DWH CITE), scikit-learn (DWH CITE), and matplotlib (DWH CITE).
